---
title: "Report Title"
subtitle: "Subtitle · Project or course name"
author: "Your Name"
date: today
date-format: "D MMMM YYYY"
lang: en  # or: nb — set logo to hvl-nb below to match

format:
  hvl-typst: default

# Named logo resource from the HVL brand. English: hvl-en · Bokmål: hvl-nb
logo: hvl-en

execute:
  echo: true
  warning: false
  message: false
---

## Introduction

This report inherits HVL colours, fonts, headings and link styling from
`_extensions/hvl-brand/brand.yml` — the same brand file that styles the
RevealJS deck in `presentation.qmd`. Nothing about the HVL visual identity is
restated in the report format itself.

Body text is set in Lora, a close open-source match to the profile font Lyon
Text. Headings use DM Sans in place of NB Akademie Std. Typst downloads both
from Google Fonts on first render and caches them, so neither font needs to be
installed locally.

## Working with the palette in R

Because the brand file is plain YAML, R can read the palette directly rather
than repeating hex codes. This keeps figures in step with the theme.

```{r}
#| label: palette
brand_path <- Sys.glob(c(
  "_extensions/hvl-brand/brand.yml", # rendering inside this repo
  "_extensions/*/hvl-brand/brand.yml" # installed via quarto add
))[1]

hvl <- yaml::read_yaml(brand_path)$color$palette
unlist(hvl[c("sea-green", "dark-blue-1", "dark-blue-2")])
```

## Figures

```{r}
#| label: fig-mpg
#| fig-cap: "Fuel efficiency against weight, coloured by cylinder count."
#| fig-height: 3.2
library(ggplot2)

ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point(size = 2.5, alpha = 0.85) +
  scale_colour_manual(
    values = unname(unlist(hvl[c("sea-green", "dark-blue-1", "dark-blue-2")])),
    name = "Cylinders"
  ) +
  labs(x = "Weight (1 000 lbs)", y = "Miles per gallon") +
  theme_minimal(base_size = 11)
```

## Tables

| Campus | Students | Programmes |
|--------|---------:|-----------:|
| Bergen | 9 800 | 62 |
| Haugesund | 2 100 | 18 |
| Sogndal | 3 400 | 24 |
| Førde | 1 200 | 9 |

: Illustrative figures only. {#tbl-campus}

## Cross-references and links

@fig-mpg and @tbl-campus show the default Typst reference styling. Links such
as [hvl.no](https://www.hvl.no) take their colour from the brand's `primary`.

Inline code like `mean(mpg)` and blocks both use JetBrains Mono:

```r
summary_df <- mtcars |>
  dplyr::group_by(cyl) |>
  dplyr::summarise(mean_mpg = mean(mpg))
```

## Extending this format

`_extensions/hvl-report/_extension.yml` is intentionally almost empty. If you
later want an HVL title page, running headers or specific page geometry, that
is where a custom `.typ` template would be wired in — brand values are readable
from Typst raw blocks as `brand-color.primary` and friends, so this brand file
stays valid.
